Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-30 paper/paper.tex
fix typos

The co-domain of binding stores @Storable@ is the same as previously defined for CESK 
machines. The conman of continuation stores @Cont@, on the other hand, is comprised of
a @Frame@ object and a continuation address @KAddr@. To mimic the run-time call stack, 
@KAddr@ plays the role of representing the remaining stack frames.
But since the continuation store may contain multiple continuations, the dereferencing 
of continuation addresses is also nondeterministic.

@@

However, since we have added nondeterminism into state, an empty list of frames means
we have reached the halt of \textit{one computation path}, and we should determine the
next state indicated by @NDCont@. Thus, we have a inner pattern matching on @ndk@:

>>>>

The co-domain of binding stores @Storable@ is the same as previously defined for CESK 
machines. The c-domain of continuation stores @Cont@, on the other hand, is comprised of
a @Frame@ object and a continuation address @KAddr@. To mimic the run-time call stack, 
@KAddr@ plays the role of representing the remaining stack frames.
But since the continuation store may contain multiple continuations, the dereferencing 
of continuation addresses is also nondeterministic.

@@

However, since we have added nondeterminism into state, an empty list of frames means
we have reached the halt of \textit{one computation path}, and we should determine the
next state indicated by @NDCont@. Thus, we have an inner pattern matching on @ndk@:
